Import_Map

### 2024-05-28 Code/Import_MapMireillePro.Rmd
Fixed map plot :)

```{r load libraries} 
library(tidyverse)
#library(lubridate)
#library(stringr)
library(broom)
#library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(data.table)
# library(googledrive)
# library(googlesheets4)
library(ggspectra)
library(photobiologyWavebands)
library(photobiology)

library("patchwork") # merging plots

@@

data_textTropicFull <- data.frame(label = c('Season:~All~year~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~Full'))
TropicFull<-ggplot() + 
  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkblue", linetype = "dashed", alpha=0.7) +
  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsTropicFull), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
TropicFull

@@

data_textTropicOMZ <- data.frame(label = c('Season:~All~year~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~OMZ'))
TropicOMZ<-ggplot() + 
  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkblue", linetype = "dashed", alpha=0.7) +
  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textTropicOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsTropicOMZ), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
TropicOMZ

@@

data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
data_textTropicFullRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
TropicFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textTropicFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textTropicFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
TropicFullRainbow

data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
data_textSummerFullRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SummerFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSummerFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSummerFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SummerFullRainbow

data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
data_textSpringFullRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SpringFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSpringFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSpringFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SpringFullRainbow

data_textWinterFullRainbowSurface <- data.frame(label = c('Near~surface'))
data_textWinterFullRainbowDeep <- data.frame(label = c('Deep:~Clade~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
WinterFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textWinterFullRainbowSurface, aes(x=500, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textWinterFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
WinterFullRainbow
```
```{r, warning = FALSE, fig.height = 12, fig.width = 6}
FullRainbow<- (TropicFullRainbow/SpringFullRainbow/SummerFullRainbow/WinterFullRainbow)
FullRainbow                         
```

```{r}
data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clades~HLI~~LLII/III~~LLIV'))
data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
TropicOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textTropicOMZRainbowSurface, aes(x=530, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textTropicOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
TropicOMZRainbow

data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clades~HLI~~LLIV'))
data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SummerOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSummerOMZRainbowSurface, aes(x=500, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSummerOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SummerOMZRainbow

data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clades~HLI~~LLII/III~~LLIV'))
data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep:~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SpringOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSpringOMZRainbowSurface, aes(x=530, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSpringOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SpringOMZRainbow

data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~LLIV'))
data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep:~Clades~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
WinterOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textWinterOMZRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textWinterOMZRainbowDeep, aes(x=480, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
WinterOMZRainbow
```
```{r, warning = FALSE, fig.height = 12, fig.width = 6}
OMZRainbow<- (TropicOMZRainbow/SpringOMZRainbow/SummerOMZRainbow/WinterOMZRainbow)
OMZRainbow                         
```

```{r, warning = FALSE, fig.height = 16, fig.width = 22}
MapCombo<-((TropicFull+TropicFullRainbow)+(TropicOMZ+TropicOMZRainbow))/((SpringFull+SpringFullRainbow)+(SpringOMZ+SpringOMZRainbow))/((SummerFull+SummerFullRainbow)+(SummerOMZ+SummerOMZRainbow))/((WinterFull+WinterFullRainbow)+(WinterOMZ+WinterOMZRainbow))
MapCombo                          
```

>>>>

```{r load libraries} 
library(tidyverse)
#library(lubridate)
#library(stringr)
library(broom)
#library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(data.table)
# library(googledrive)
# library(googlesheets4)
library(ggspectra)
library(photobiologyWavebands)
library(photobiology)
library(ggforce) #ellipse
library("patchwork") # merging plots

@@

data_textTropicFull <- data.frame(label = c('Season:~All~year~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~Full'))
TropicFull<-ggplot() + 
  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkblue", linetype = "dashed", alpha=0.9, size = 1) +
  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textTropicFull, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsTropicFull), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
TropicFull

@@

data_textTropicOMZ <- data.frame(label = c('Season:~All~year~~~~~~~~Daylight:~12~h~~~~~~~~Oxygen:~OMZ'))
TropicOMZ<-ggplot() + 
  geom_rect(data=d5, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "transparent", color="darkblue", linetype = "dashed", alpha=0.9, size = 1) +
  geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
  geom_rect(data=d3, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "lightskyblue1", color="lightskyblue3", alpha=0.5) +
  geom_map(data = world_coordinates, map = world_coordinates, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
  geom_text(data=data_textTropicOMZ, aes(x=0, y=110, label=label), size=4.5, parse=TRUE) +
  scale_y_continuous(breaks=seq(-90, 90, by = 45)) +
  coord_cartesian(ylim = c(-90, 120)) +
  labs(y = "Latitude", x = "Longitude") +
  #ggh4x::facet_nested(cols = vars(facetsTropicOMZ), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=14),
        axis.title = element_text(size=18),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        axis.title.y = element_text(margin=margin(r=10)),
        #axis.title.x = element_text(margin=margin(t=10)),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=14))
TropicOMZ

@@

data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~HLI'))
data_textTropicFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
TropicFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textTropicFullRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
  geom_text(data=data_textTropicFullRainbowDeep, aes(x=515, y=90, label=label), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
TropicFullRainbow

data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~HLI'))
data_textSpringFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SpringFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSpringFullRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
  geom_text(data=data_textSpringFullRainbowDeep, aes(x=515, y=90, label=label), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SpringFullRainbow

data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~HLI'))
data_textSummerFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SummerFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSummerFullRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
  geom_text(data=data_textSummerFullRainbowDeep, aes(x=515, y=90, label=label), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SummerFullRainbow

data_textWinterFullRainbowSurface <- data.frame(label = c('Near~surface~(180~µE)'))
data_textWinterFullRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clade~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
WinterFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textWinterFullRainbowSurface, aes(x=470, y=215, label=label), size=4.5, parse=TRUE) +
  geom_text(data=data_textWinterFullRainbowDeep, aes(x=475, y=90, label=label), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
WinterFullRainbow
```
```{r, warning = FALSE, fig.height = 12, fig.width = 6}
FullRainbow<- (TropicFullRainbow/SpringFullRainbow/SummerFullRainbow/WinterFullRainbow)
FullRainbow                         
```

```{r}
data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clades~HLI~~LLII/III~~LLIV'))
data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
TropicOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textTropicOMZRainbowSurface, aes(x=535, y=215, label=label), size=4.5, parse=TRUE) +
  geom_text(data=data_textTropicOMZRainbowDeep, aes(x=510, y=90, label=label), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
TropicOMZRainbow

data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clades~HLI~~LLII/III~~LLIV'))
data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SpringOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSpringOMZRainbowSurface, aes(x=535, y=215, label=label), size=4.5, parse=TRUE) +
  geom_text(data=data_textSpringOMZRainbowDeep, aes(x=510, y=90, label=label), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SpringOMZRainbow

data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clades~HLI~~LLIV'))
data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~HLI~~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SummerOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSummerOMZRainbowSurface, aes(x=515, y=215, label=label), size=4.5, parse=TRUE) +
  geom_text(data=data_textSummerOMZRainbowDeep, aes(x=510, y=90, label=label), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SummerOMZRainbow

data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface~(180~µE):~Clade~LLIV'))
data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep~(30~µE):~Clades~LLII/III~~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
WinterOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  geom_ellipse(aes(x0 = 555, y0 = 143, a = 164, b = 28, angle = pi / 10), fill = "white", colour = "white") +
  coord_fixed() +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textWinterOMZRainbowSurface, aes(x=500, y=215, label=label), size=4.5, parse=TRUE) +
  geom_text(data=data_textWinterOMZRainbowDeep, aes(x=500, y=90, label=label), size=4.5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
WinterOMZRainbow
```
```{r, warning = FALSE, fig.height = 12, fig.width = 6}
OMZRainbow<- (TropicOMZRainbow/SpringOMZRainbow/SummerOMZRainbow/WinterOMZRainbow)
OMZRainbow                         
```
